Evolution Reinforces Cooperation with the Emergence of Self-Recognition Mechanisms: an empirical study of the Moran process for the iterated Prisoner's dilemma

### 2017-07-20 main.tex

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an empirical study of the Moran process for the iterated
       Prisoner's dilemma using reinforcement learning}
\author{Vincent Knight \and
        Marc Harper \and
        Nikoleta E. Glynatsi \and
        Owen Campbell} % TODO Authors?
\date{}

>>>>

% Title
\title{Evolution Reinforces Cooperation with the Emergence of Self-Recognition
       Mechanisms: an empirical study of the Moran process for the iterated
       Prisoner's dilemma}
\author{Vincent Knight \and
        Marc Harper \and
        Nikoleta E. Glynatsi \and
        Owen Campbell} % TODO Authors?
\date{}
